---
title: "practice"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(palmerpenguins)
```

command option i creates r ticks for code chunks
```{r}
me <- "Isabella"
b <- 3
a <- 3L
list(me, a, b)
whatvariable <-class(me)

```

practiced concatenation: tried to think about what R coerces the variables to be
1. characters
2. number
3. number
1:3 means list 1 2 3
4. number
5. boolean 

I ran str() first and then class(),

lets try it out with the code she gave in class they are in order 

```{r}
c1 <- c(1, NA+1L, "C")
c2 <- c(1L / 0, NA)
c3 <- c(1:3, 5)
c4 <- c(3L, NaN+1L)
c5 <- c(NA, TRUE)
```
using comparison operators to assign variables 
```{r}
var_30 <- 15 + 15
true_var <- 5 < 6
print(var_30)
print(true_var)
paste(var_30, true_var)
```
case_when() example
what happens if i only specify when i change a to A
create tibble and then test out case_when
```{r}
test <- tibble(x = 1:3, y = c("a", "b", "c"))

test |> 
  mutate(new_col = case_when(y == "a" ~ "A"))
# once one row has something thats true it doesnt look at any other conditions in the data set 

bike <- read_csv2("https://raw.githubusercontent.com/COGS137/datasets/main/nc_bike_crash.csv", 
                  na = c("NA", "", "."))
#she asks us to see how many accidents in our dataset required an ambulance ride and had the crash type "bicyclist lost control - mechanical problems, my code:

temp <- bike |>
    filter(AmbulanceR == "Yes")
 temp <- temp |> filter(Crash_Type == "Bicyclist Lost Control - Mechanical Problems")
nrow(temp)

#how she did it: 
#group_by(Crash_Type) |> 
# summarise (number = n())

 
```
last thing from lecture
"he wants all hike accidents from his County (Cumberland), but he only wants to know the road's speed limit, the age of the biker, and if alcohol was involved. 

```{r}
for_boss<- bike |> 
  filter(County == "Cumberland")
for_boss <- for_boss |>
    select(Speed_Limi, Bike_Alc_D, Bike_Age)
```

lecture 8: 10/11/21
install the package "palmerpenguins"
looking at ggplot2
aes creates an aesthetic 
labs creates labels 

```{r}
  #install.packages("ggplot2")
#install.packages("palmerpenguins")
#library(palmerpenguins)
glimpse(penguins)

ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species)
) +
  geom_point() +
  labs(
    title = "FLipper Length and Body Mass",
    subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo",
    x = "Flipper Length (mm)",
    y = "Body Mass (g)",
    color = "Species",
    caption = "Source: Palmer Penguins"
  )
#default for caption is bottom right 
# you can also pipe the data into ggplot |>
```
lecture 12: characterizing relationships with models
```{r}
pp <- read_csv("https://raw.githubusercontent.com/COGS137/datasets/main/paris_paintings.csv", na = c("n/a", "", "NA"))


```